

\documentclass[letterpaper, 12 pt]{article}

\usepackage[margin= 1cm]{geometry}
\usepackage{tabularx}
\usepackage{fontspec}
\usepackage{blindtext}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage{multicol}
\usepackage{nopageno}

%------Manual setting
\setmainfont{Calibri}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*}
\titleformat{\section}{\vspace{-5pt}\large}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]


\begin{document}
		% -------------------- HEADING--------------------
		\begin{flushright}
			\texttt{created using {\LaTeX}}
		\end{flushright}
		\vspace*{-1cm}
		\begin{center}
			\textbf{\Huge Rahul Sinha} \\ \vspace{4pt}
			\faIcon{github}
			\href{https://github.com/rahulsinhabspr}{\underline{https://github.com/rahulsinhabspr}} $  $
			\faIcon{linkedin}
			\href{www.linkedin.com/in/rahulsinhabspr}{\underline{www.linkedin.com/in/rahulsinhabspr}} $  $
			\faIcon{envelope}
			\href{mailto:rahulsinhabspr@live.com}
			{\underline{rahulsinhabspr@live.com}}
			\newline
			\faIcon{certificate}
			\href{https://www.credly.com/users/rahul-sinha.eb04cee7}{$\underline{Credly}$}
			\faIcon{mobile}
			{$\underline{+91-7401361223}$}
			\faIcon{home}
			{$\underline{Bengaluru}$}
		\end{center}
		
	\section*{Professional Summary}
			\begin{itemize}[noitemsep]
				\item {More than 9 years' experience as a Tivoli Monitoring Administrator, SCOM Administrator, Systems Administrator, Application Support Specialist, and Technical Support Specialist.}
				\item {Developed multiple shell scripts and PowerShell scripts to automate bulk requests and reduce workload.}
				\item {Recreated LDAP authentication software using C\#, Soap Request, and PowerShell for the Ticketing Tool (Maximo).}
				\item  {Completed a substantial amount of web development work, which allowed my wife to increase her earnings.}
				\item {Retained many Symantec customers and helped them renew their subscriptions, which resulted in economic benefits for the company.}
				\item {Received approval and sent 2 technical feedback and 1 installation process change to Symantec.}
				\item {Use to perform DSAT. analysis on the Symantec VSS team.}				
			\end{itemize}
				% -------------------- SKILLS --------------------
			\section*{Skills}
			\begin{tabular}{m{0.25\textwidth} m{0.70\textwidth}} 
				\textbf{Back End Development} & Python, PowerShell, Shell Scripting, PHP, C\#, \LaTeX.  \\ 
				\textbf{Front End Development} & HTML, CSS, JavaScript, JQuery, WordPress. \\
				\textbf{Server Support} & Windows Server 2012, Active Directory, IBM Domino Server, IBM Notes. \\
				\textbf{Application Support} & IBM Tivoli Monitoring(ITM 6), Microsoft System Center Operations Manager (SCOM 2012), Cisco (Gemalto) , Novell Imanager, Norton. \\ 
				\textbf{Technical Support} & Windows, Mac OS, Android Phone. \\ 
				\textbf{Ticketing Tool (Maximo)} & Administration, Integration, Automation using Python, Scheduler, Workflow, Application Creation, Dialog box Creation, Asset Management. \\
				\textbf{Network Support (Cisco)} & Networking Concept,Packet Tracer \& GNS3 simulator, configuration and troubleshooting STP, DHCP, ARP, NAT, ACL, port security, creating VLAN,
				Trunks, IPv6, Routing Protocol (Static, RIP, OSPF, EIGRP, BGP).\\
			\end{tabular}		
		\section*{Experience}
		\begin{itemize}[noitemsep]
			\item {\textbf{Kyndryl Solutions Pvt. Ltd.}$|$ \textit{ITM Administrator, ITM-6} \hfill {Sep. 2021 -- Present}}\\
			\vspace*{-0.6cm}
			\begin{itemize}[noitemsep]
				\item {Configuring and Managing HubTems, RTEMS, TEPS and BlueCare.}
				\item {Managing Netcool Probes, Auto ticketing, and Alert Mapping.}
				\item {Installation, Configuring and Uninstall of Tivoli Agents in (Windows, Linux, AIX, VIOS, ESX, Cisco UCS, Domino Servers, Vmware and Oracle Servers.}
				\item {Built client-specific situations/alerts.}
			\end{itemize}
			\vspace*{-0.1cm}
			\item {\textbf{IBM India Pvt. Ltd.}$|$ \textit{SCOM Administrator, SCOM-2012} \hfill {Dec. 2019 -- Aug. 2021}}\\
			\vspace*{-0.6cm}
			\begin{itemize}[noitemsep]
				\item {Configuring and Managing SCOM-2012 Operations Manager and Data Warehouse.}
				\item {Installation, Modification and Uninstall of SCOM Agents, SCOM Gateway Servers and  SCOM Management Pack.}
				\item {SCOM Custom Management Pack creation, modification, and deletion.}
				\item {Overriding Rules/Monitors based on Customer Requirements in SCOM-2012 Operations Manager.}
				\item {Built client-specific dashboard for the SCOM Web Interface.}
				\item {Renewal of Certificates in SCOM Gateway Servers.}	
			\end{itemize}
			\vspace*{-0.1cm}
			\item {\textbf{IBM India Pvt. Ltd.}$|$ \textit{System Administrator, Active Directory, IBM Domino Server}	\hfill{Feb. 2016 -- Nov. 2019}}\\
			\vspace*{-0.6cm}
			\begin{itemize}[noitemsep]
				\item{Distribution List, Mailin Database, and Domino Access Group creation, deletion, and maintenance.}
				\item {User Management and Certificate Management in IBM Lotus Notes.}
				\item {ID and user certificate creation, deletion, and maintenance for IBM Lotus Notes.}
				\item {Managing and deleting user data in Novell Imanager.}
				\item {Active Directory user and group administration.}
				\item {User management in Cisco VPN (Gemalto) and Novell Imanager.}
				\item {File and folder services, group policy management, access to terminal servers, and RDP access on Windows Server.}	
			\end{itemize}
			\vspace*{-0.1cm}
			\item {\textbf{Sutherland Global Services}$|$ \textit{Consultant, NortonLive VSS}\hfill{June 2014 -- Feb. 2016}}\\
			\vspace*{-0.6cm}
			\begin{itemize}[noitemsep]
				\item {Provided technical support to Symantec (NortonLive Spyware and Virus Removal Services) End Users.}
				\item {Had the opportunity to mentor the new hire, where I provide technical feedback to new hires.}
				\item {Received multiple awards for being the Topper of the process and had the chance to meet with site HR and have coffee with him.}
				\item  {Received multiple awards for best performance, including zero DSAT. in a month and best feedback from the customer.}
		\end{itemize}
		
	\end{itemize}
		% -------------------- IT Certificate \& Courses--------------------
		\section{IT Certificate \& Courses Completed}
			\begin{itemize}[noitemsep]
				\item {Completed all the Maximo Courses: \href{https://www.credly.com/badges/63308385-9f62-46dd-bcf4-7ae85141417f/public_url}{IoT - Maximo Introduction and Overview}, \href{https://www.credly.com/badges/b30f2751-e9e7-48d7-a2b5-05554d597b8a/public_url}{IoT - Maximo Security Model}, \href{https://www.credly.com/badges/83f47a44-e89e-4e09-a9d1-18c5e1962e2a/public_url}{IoT - Maximo Asset Management}, \href{https://www.credly.com/badges/d5e89db9-447e-40d0-b15c-430ecd9a0820/public_url}{IoT - Maximo Domains}, \href{https://www.credly.com/badges/b3788bc2-5080-4e01-a80c-de9fd194956f/public_url}{IoT - Maximo Database Configuration}, \href{https://www.credly.com/badges/cad42cb1-bfc4-41da-9f38-25278f68f5a7/public_url}{IoT - Maximo Workflow}, \href{https://www.credly.com/badges/7a6d6602-a0ae-4cd7-8e84-f5982149b181/public_url}{IoT - Maximo 7.6 New Features}.} 
				\item {Completed \href{https://www.credly.com/badges/94135bf2-5cd9-4cfe-b940-723479544e3f/public_url}{IBM Agile Explorer Course}.} 
				\item {Completed \href{https://www.credly.com/badges/0259d635-d864-4236-8872-a44eea7ab29c/public_url}{IBM Cloud Private Infrastructure and Architecture Course}.} 
				\item {Completed many Leadership courses:\href{https://www.credly.com/badges/af521083-272b-4373-bf01-cf65bbf0251d/public_url}{Leadership Behavior - Fast}, \href{https://www.credly.com/badges/e478b3ff-6f6e-4350-89f9-f3822a450df3/public_url}{Leadership Behavior - Flat}, \href{https://www.credly.com/badges/afa9f307-dce4-48c5-9a2b-24dc7831d602/public_url}{Leadership Behavior - Empathetic}, \href{https://www.credly.com/badges/bbac771c-7f96-4bb6-b89a-8a7f89ba070a/public_url}{Leadership Behavior - Devoted}, \href{https://www.credly.com/badges/0eb16b26-7eba-440e-b657-f8e9715af76c/public_url}{Leadership Behavior - Restless}, \href{https://www.credly.com/badges/899c9aed-17a5-4eca-a8b0-1e132c289225/public_url}{Leadership Behavior - Advocate}.}
				\item {ScienceLogic Certified Professional eLearning (certification number 60619766.)} 
				\item {Cisco Certified Entry Networking Technician (CCENT : CSCO12750446.)} 
				\item {Completion of Microsoft Official Course: Configuring and Troubleshooting a windows server 2008 Network Infrastructure 6421AS in 2013.} 
				\item {Completion of Microsoft Official Course: Planning \& Administering Windows server 2008 Servers in 2013.}
				\item {Course Completion Certificate of Certified Ethical Hacking in 2013.}
				\item {Certificate of Participation in 2013 in Life Skills Training Program from The Bridge Training and Development.}
			\end{itemize}
		
			\section{Education}
				\begin{itemize}[noitemsep]
					\item {{Indian Institute of Information Technology Design and Manufacturing, Kancheepuram} \hfill {May 2014}\\{Master of design, Communication Systems} \hfill {7.55(CGPA)}} 
					\item {Bhilai Institute of Technology, Durg $|$ \textit{affiliated to CSVTU}} \hfill {June 2009}\\{Bachelor of Technology, Electronics and Telecommunication Engineering} \hfill {60.23\%}
					\item  {{D.A.V Public School, Bishrampur} \hfill {2005}\\{Class XII} \hfill {79.80\%}}
					\item {{D.A.V Public School, Bishrampur} \hfill {2003}\\ {ClassXII} \hfill {82.33\%}}		
					
				\end{itemize}
			% -------------------- Awards--------------------
			\section{Awards}
				\begin{itemize}[noitemsep]
					\item {Received certificate for putting Client First in IBM.}
					\item {Topped inter branch project exhibition in B.I.T (2007).}
					\item {Topped all India Mathematics Examination organized by Together with in 2005.}
				\end{itemize}
		
		%----------------------Design and Quality Courses
		\section{Design and Quality Courses}
			\begin{itemize}[noitemsep]
				\item Design for Quality \& Reliability
				\item Green Energy \& Product Design
				\item Product Conceptualization and visualization
				\item Product Design Practice and Prototyping
				
			\end{itemize}
	
		%----------------------Additional Information-------------------
		\section{Additional Information}
			\begin{tabular}{m{0.25\textwidth} m{0.70\textwidth}}
				\textbf{Date of Birth} & $15^{th} June 1987$  \\
				\textbf{Parents} & Shailendra Kumar Sinha \& Taruna Sinha  \\
				\textbf{Hobbies} & Repairing Electronics Devices (Computer,Mobile \& Laptop)   and Playing Computer games  \\	
			\end{tabular}
			

		
\end{document}


