
\documentclass[letterpaper, 12pt]{article}

\usepackage[margin= 1cm]{geometry}
\usepackage{tabularx}
\usepackage{fontspec}
\usepackage{blindtext}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}


%------Manual setting
\setmainfont{Calibri}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*}
\titleformat{\section}{\vspace{-5pt}\large}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]


\begin{document}
	
	% -------------------- HEADING--------------------
	\begin{flushright}
		\texttt{created using {\LaTeX}}
	\end{flushright}
	\vspace*{-1cm}
	\begin{center}
		\textbf{\Huge Rahul Sinha} \\ \vspace{4pt}
		\faIcon{github}
		\href{https://github.com/rahulsinhabspr}{\underline{https://github.com/rahulsinhabspr}} $  $
		\faIcon{linkedin}
		\href{www.linkedin.com/in/rahulsinhabspr}{\underline{www.linkedin.com/in/rahulsinhabspr}} $  $
		\faIcon{envelope}
		\href{mailto:rahulsinhabspr@live.com}
		{\underline{rahulsinhabspr@live.com}}
		\newline
		\faIcon{mobile}
		{$\underline{+91-7401361223}$}
		\faIcon{home}
		{$\underline{Bengaluru}$}
	\end{center}
	% --------------------Professional Summary --------------------
	\section*{Professional Summary}
	\textnormal{More than 9 years' experience as a Tivoli Monitoring Administrator, SCOM Administrator, Systems Administrator, Application Support Specialist, and Technical Support Specialist. Developed multiple shell scripts and PowerShell scripts to automate bulk requests and reduce workload. Recreated LDAP authentication software using C\#, Soap Request, and PowerShell for the Ticketing Tool (Maximo). Designed alert detail reports for the Platform Team. Created and modified alerts for Linux, AIX, and Windows servers.} 
	% -------------------- SKILLS --------------------
	\section*{Skills}
		\begin{tabular}{m{0.25\textwidth} m{0.75\textwidth}} 
			\textbf{Back End Development} & Python,PowerShell,Shell Scripting,PHP,C\#,\LaTeX.  \\ 
			\textbf{Front End Development} & Html,css,JavaScript,JQuery. \\
			\textbf{Server Support} & Windows Server 2012, Active Directory,IBM Domino Server, IBM Notes. \\
			\textbf{Application Support} & IBM Tivoli Monitoring(ITM 6), Microsoft System Center Operations Manager (SCOM 2012), Cisco (Gemalto) , Novell Imanager, Norton. \\ 
			\textbf{Technical Support} & Windows, Mac OS, Android Phone. \\ 
		\end{tabular}
% -------------------- EXPERIENCE --------------------
	\section*{Experience}
		\begin{itemize}[noitemsep]
			\item {\textbf{Kyndryl Solutions Pvt. Ltd.}$|$ \textit{ITM Administrator, ITM-6} \hfill {Sep. 2021 -- Present}}\\
		 			\vspace*{-0.6cm}
				\begin{itemize}[noitemsep]
					\item {Configuring and Managing HubTems, RTEMS, TEPS and BlueCare.}
					\item {Managing Netcool Probes, Auto ticketing, and Alert Mapping.}
					\item {Installation, Configuring and Uninstall of Tivoli Agents in (Windows,Linux, Aix, vios ESX,Cisco ucs,Domino,Vmware and oracle Servers.}
					\item {Built client-specific situations/alerts.}
				\end{itemize}
				\vspace*{-0.1cm}
				\item {\textbf{IBM India Pvt. Ltd.}$|$ \textit{SCOM Administrator, SCOM-2012} \hfill {Dec. 2019 -- Aug. 2021}}\\
				\vspace*{-0.6cm}
				\begin{itemize}[noitemsep]
					\item {Configuring and Managing SCOM-2012 Operations Manager and Data Warehouse.}
					\item {Installation, Modification and Uninstall of SCOM Agents, SCOM Gateway Servers and  SCOM Management Pack.}
					\item {SCOM Custom Management Pack creation, modification, and deletion.}
					\item {Overriding Rules/Monitors based on Customer Requirements in SCOM-2012 Operations Manager.}
					\item {Built client-specific dashboard for the SCOM Web Interface.}
					\item {Renewal of Certificates in SCOM Gateway Servers.}	
				\end{itemize}
				\vspace*{-0.1cm}
				\item {\textbf{IBM India Pvt. Ltd.}$|$ \textit{System Administrator, Active Directory, IBM Domino Server}	\hfill{Feb. 2016 -- Nov. 2019}}\\
				\vspace*{-0.6cm}
				\begin{itemize}[noitemsep]
					\item{Distribution List, Mailin Database, and Domino Access Group creation, deletion, and maintenance.}
					\item {User Management and Certificate Management in IBM Lotus Notes.}
					\item {ID and user certificate creation, deletion, and maintenance for IBM Lotus Notes.}
					\item {Managing and deleting user data in Novell Imanager.}
					\item {Active Directory user and group administration.}
					\item {User management in Cisco VPN (Gemalto) and Novell Imanager.}
					\item {File and folder services, group policy management, access to terminal servers, and RDP access on Windows Server.}	
				\end{itemize}
				\vspace*{-0.1cm}
				\item {\textbf{Sutherland Global Services}$|$ \textit{Consultant, NortonLive VSS}\hfill{June 2014 -- Feb. 2016}}\\
				\vspace*{-0.6cm}
				\begin{itemize}[noitemsep]
					\item {Provided technical support to Symantec (NortonLive Spyware and Virus Removal Services) End Users.}
					\item {Retained many Symantec customers and assisted them to renew the subscription which benefited the company economically.}
					
				\end{itemize}
		\end{itemize}  

		% -------------------- EDUCATION --------------------
	\section{Education}
		\begin{itemize}[noitemsep]
			\item {{Indian Institute of Information Technology Design and Manufacturing, Kancheepuram} \hfill {May 2014}\\{Master of design, Communication Systems} \hfill {7.55(CGPA)}} 
			\item {Bhilai Institute of Technology, Durg $|$ \textit{affiliated to CSVTU}} \hfill {June 2009}\\{Bachelor of Technology, Electronics and Telecommunication Engineering} \hfill {60.23\%}
			\item  {{D.A.V Public School, Bishrampur} \hfill {2005}\\{Class XII} \hfill {79.80\%}}
			\item {{D.A.V Public School, Bishrampur} \hfill {2003}\\ {ClassXII} \hfill {82.33\%}}		
		
		\end{itemize}
	
		% -------------------- IT Certificate \& Courses--------------------
	\section{IT Certificate \& Courses Completed}
		\begin{itemize}[noitemsep]
			\item {Cisco Certified Entry Networking Technician (CCENT : CSCO12750446.)}
			\item {ScienceLogic Certified Professional eLearning (certification number 60619766.)}
			\item {Completion of Microsoft Official Course: Configuring and Troubleshooting a windows server 2008 Network Infrastructure 6421AS in 2013.}
			\item {Completion of Microsoft Official Course: Planning \& Administering Windows server 2008 Servers in 2013.}
			\item {Course Completion Certificate of Certified Ethical Hacking in 2013.}
			\item {Certificate of Participation in 2013 in Life Skills Training Program from The Bridge Training and Development.}
		\end{itemize}
		
		
		
		\begin{minipage}{0.5\textwidth}
		
				% -------------------- EDUCATION --------------------
			\section{Education}
				\begin{itemize}[noitemsep]
					\item {{IIITD\&M, Kancheepuram} \hfill {May 2014}\\{MDES, Communication Systems} \hfill {7.55(CGPA)}} 
					\item {BIT, Durg} \hfill {June 2009}\\{BE, Electronics and Telecommunication} \hfill {60.23\%}
					\item  {{D.A.V Public School, Bishrampur} \hfill {2005}\\{Class XII} \hfill {79.80\%}}
					\item {{D.A.V Public School, Bishrampur} \hfill {2003}\\ {ClassXII} \hfill {82.33\%}}
				\end{itemize}		
		\end{minipage}\hfil
	\begin{minipage}{0.45\textwidth}
			% -------------------- Awards--------------------
		\section{Awards}
		\begin{itemize}[noitemsep]
			\item {Received certificate for putting Client First in IBM.}
			\item {Topped inter branch project exhibition in B.I.T (2007).}
			\item {Topped all India Mathematics Examination organized by Together with in 2005.}
		\end{itemize}
		
	\end{minipage}	
		
		
		
		
		
		
		
					
\end{document}

